---
title: "NW coding assignment"
author: "Lorenzo Duran"
date: "2024-01-31"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(readr)
library(ggplot2)
library(knitr)
trades <- read_csv("Downloads/trades.csv",
                   show_col_types = FALSE, 
                   col_types = cols(trans_date = col_date(format = "%m/%d/%Y")))

```

```{r}
library(dplyr)
library(tidyr)
trades1 = trades %>% 
  filter(trans_date >= "2023-01-01" & trans_date <= "2023-04-30") %>% 
  distinct()

```

```{r}
trades2 = trades1 %>% 
  mutate(sums = case_when(trans_type == "A" ~ shares,
                          trans_type == "D" ~ -1 * shares))

```

```{r}
table1 = trades2 %>% 
  group_by(ticker) %>% 
  summarise(net_shares = sum(sums),
            total_trades = n(),
            percent_traded = (mean(shares/(shares + shares_owned)))*100,
            net_profits = sum(sums*-1 * price, na.rm = T))
```

```{r}
kable(sample_n(table1,10))
```
I included in the table the number of trades realized during this period
as wellas the amount of shares transacted as a percentage of the number
of shares held before the transaction defined as:

$$mean(\frac{shares}{shares + shares\_owned})$$

I think this would be a useful indicator of trade volumes
with respect to stock holdings. 

I have also included a measure for the profits taken
during this period defined as:

$$\sum shares\_disposed * sell\_price - \sum shares\_aquired * buy\_price$$

Where a positive number indicates more profits, as the ticker is being sold
more or at a higher price. Therefore, this table now includes information on
the net number of shares transacted, a measure of the frequency of transactions
during this period, a measure of the volume of shares transacted with respect
to previous share holdings and a measure for the amount of profit taken during
this period. 


```{r, warning = F}
stocks <- read_csv("Downloads/stocks_Jan-Nov2023.csv",show_col_types = FALSE, 
                   col_types = cols(date = col_date(format = "%m/%d/%Y")))
stocks1 = stocks %>% 
  distinct()
```

```{r}
returns_graph = function (dates, ticker1, starting){
  data = stocks %>%
    filter(TICKER == ticker1 & date >= dates[1] & date <= as.Date(dates[2])+1)
  value = c(starting)
  for (i in data$RET[2:nrow(data)]){
  value = append(value, value[length(value)]*(1+i))
  }
  ggplot(data[1:nrow(data)-1,],aes(x = data$date[1:nrow(data)-1])) +
    geom_line(aes(y = value[1:length(value)-1], color = "Investment Value"))+
  geom_hline(yintercept = starting,
             aes(color = "Initial Value"),linetype="dotted")+
  theme_classic()+theme(legend.position = "top")+
  theme(panel.grid.major.y = element_line(),
        panel.grid.minor.y = element_line())+
  labs(title = paste("Value of", toString(starting), "invested in",
                     ticker1,"from",dates[1],"to",dates[2],  sep = " "),
       x = "Date", y = "Value of Investment in USD", color = "", 
       subtitle = paste(
         paste("Final Value in USD:",
               toString(round(value[length(value)-1],2))),
         paste("Cumulative Return: ",
               toString(round((value[length(value)-1]-starting)/starting, 4))),
         sep = "\n"))+
  theme(axis.title = element_text(size=11,family = "serif"),
        plot.title = element_text(size=15,family = "serif", face = "bold"),
        legend.text = element_text(size=10,family = "serif"),
        plot.subtitle = element_text(size=11,family = "serif"),
        plot.caption = element_text(size = 8,family = "serif", hjust= 0))+
  scale_color_manual(values=c('steelblue', 'black'))
}
```


```{r,warning=FALSE}
returns_graph(c("2023-02-01","2023-08-31"),"PFE",10000)
```
```{r}
table2 = stocks1 %>%
  filter(date >= as.Date("2023-05-01")+1 & date < "2023-11-30") %>% 
  group_by(TICKER) %>% 
  summarise(cumulative_return_RET = prod(1 + RET, na.rm = T)-1)
```

```{r}
kable(sample_n(table2,10))
```
I calculated returns based on the RET values on the original data and then
spot-checked my results using online calculators
like https://www.dividendchannel.com/drip-returns-calculator/


```{r, warning = F}
footnotes <- read_csv("Downloads/footnotes.csv", show_col_types = FALSE)
footnotes1 = footnotes %>% 
  distinct()
```

```{r}
dates1 = trades1%>%
  filter(trans_date >= "2023-01-01" & trans_date <= "2023-04-30") %>%
  distinct(accession_num, .keep_all = T) %>% 
  select(accession_num, trans_date)
```

```{r}
footnotes2 = right_join(dates1,footnotes1, by = "accession_num")
```


```{r}
footnotes3 = footnotes2 %>% 
  mutate("10b5-1" = case_when(grepl("10(b)5-1", text, fixed = T)~1,
                              grepl("10(b)5-1", text, fixed = F) ~ 0))
```

```{r}
footnotes3 %>% 
  filter(trans_date >= "2023-01-01" & trans_date <= "2023-04-30") %>% 
  summarise('10(b)5-1' = sum(`10b5-1`, na.rm = T)) %>% 
  kable()
```

```{r}
has_10b51_ = footnotes3 %>% 
  filter(trans_date >= "2023-01-01" & trans_date <= "2023-04-30") %>% 
  filter(`10b5-1` == 1)
```

```{r}
kable(has_10b51_[,c("trans_date", "accession_num", "text")])
```
```{r}
has_10b51_all = footnotes3 %>%
  filter(`10b5-1` == 1)
kable(sample_n(has_10b51_all[,c("trans_date", "accession_num", "text")],10))
```

I looked into the original csv as a text file and also found 64 occurrences of
10(b)5-1, which tells me that the search function for "10(b)5-1" is working
properly. And the date filtering was done in a similar style as before,
so its reliability has been shown in previous exercises. 
